FLM for growth as function of SPEI

### 2021-01-15 analysis/paper/vital rate models.Rmd
switch to maximum lag of 36 months

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, paged.print=FALSE)
library(tidyverse)
library(here)
library(mgcv)
library(dlnm)
library(bbmle)
library(lubridate)
library(glue)
library(patchwork)
library(sf)
library(tsibble)
library(broom)

@@

- 
- ~~Remove seedlings from dataset, for now~~
- ~~Separate models for CF and fragment, for now~~
- Add model for probability of reproduction and other vital rates
- Model seedlings separately?
- Add random effects, interactions, other complexities
- Try integrative measure of size.  Some paper you read did some formula with height and leaf number. Plantago?

@@

```{r}
length(unique(demog$ha_id_number))
range(demog$year)
2009-1998
```

@@

```{r}
demog_full <-
  demog_full %>% 
  mutate(log_shts = log(shts + 0.0001), .after = shts) %>% 
  mutate(log_shts_next = log(shts_next + 0.0001), .after = shts_next)
```

@@

```{r}
g_post_cf <-
  gam(shts_next ~ 
        s(log_shts) + 
        s(plot, bs = "re") + #random effect of plot
        s(spei_history, L,
          bs = "cb",
          k = c(3, 25),  #unimodal-ish response to drought, but one knot per month lag.
          xt = list(bs = "cr")),
      family = scat(link = "log"),
      data = demog_post_cf,
      # gamma = 1.2, #I maybe need to optimize this with cross-validation?
      method = "REML")
```

@@

```{r}
gam.check(g_post_cf) 
```

@@

```{r}
g_post_1ha <-
  gam(shts_next ~ 
        s(log_shts) +
        s(plot, bs = "re") +
        s(spei_history, L,
          bs = "cb",
          k = c(3, 25),  #unimodal response to drought, but one knot per month lag.
          xt = list(bs = "cr")),
      family = scat(link = "log"),
      data = demog_post_1ha,
      # gamma = 1.2, #increases smoothness when above 1
      method = "REML")
```

```{r}
gam.check(g_post_1ha)
```

Looks great

@@

```{r}
p_growth_cf <-
  pred_g_post_cf %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = exp(fitted), fill = exp(fitted))) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:24, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "Month",
      labels = month(ymd("2020-2-01") - months(0:24), label = TRUE))
  ) +
  scale_x_continuous("SPEI_3", expand = c(0,0)) +
  scale_fill_viridis_c("#shoots (t+1)", option = "A", limits = exp(shoot_lim)) +
  labs(title = "Continuous Forest",
       caption = glue("Predicted values for average sized plant ({mean_size} shoots)")) +
  theme_bw()
p_growth_cf
```

```{r}
p_growth_1ha <-
  pred_g_post_1ha %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = exp(fitted), fill = exp(fitted))) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:24, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "Month",
      labels = month(ymd("2020-2-01") - months(0:24), label = TRUE))
  ) +  scale_x_continuous("SPEI_3", expand = c(0,0)) +
  scale_fill_viridis_c("#shoots (t+1)", option = "A", limits = exp(shoot_lim)) +
  labs(title = "1-ha Fragments",
       caption = glue("Predicted values for average sized plant ({mean_size} shoots)")) +
  theme_bw()
p_growth_1ha
```

@@

```{r}
p_growth_cf_slice <-
  pred_g_post_cf %>% 
  filter(nearest(x, -1.50)) %>% 
  ggplot(aes(x = lag, y = exp(fitted))) +
  geom_ribbon(aes(
    ymin = exp(fitted - se.fit * 1.96),
    ymax = exp(fitted + se.fit * 1.96)
  ), alpha = 0.3)+
  geom_line() +
  scale_x_continuous("lag(months)", breaks = 0:24) +
  labs(title = "Continuous Forest", y = "shoots (t+1)") +
  theme_linedraw()
p_growth_cf_slice
```

```{r}
p_growth_1ha_slice <-
  pred_g_post_1ha %>% 
  filter(nearest(x, -1.5)) %>% 
  ggplot(aes(x = lag, y = exp(fitted))) +
  geom_ribbon(aes(
    ymin = exp(fitted - se.fit * 1.96),
    ymax = exp(fitted + se.fit * 1.96)
  ), alpha = 0.3)+
  geom_line() +
  scale_x_continuous("lag(months)", breaks = 0:24) +
  labs(title = "1-ha Fragments", y = "shoots (t+1)") +
  theme_linedraw()
p_growth_1ha_slice
```

@@

```{r}
s_post_cf <-
  gam(surv ~ 
        s(log_shts) +
        s(plot, bs = "re") +
        s(spei_history, L,
          bs = "cb",
          k = c(3, 25),  #cubic response (at most) to drought, one knot per month lag.
          xt = list(bs = "cr")),
      family = binomial,
      data = demog_post_cf,
      # gamma = 1.2, #increases smoothness when above 1
      method = "REML")
```
```{r}
# gam.check(s_post_cf) #not sure what to expect from any of these plots
```
```{r}
summary(s_post_cf)
```

```{r}
s_post_1ha <-
  gam(surv ~ 
        s(log_shts) +
        s(plot, bs = "re") +
        s(spei_history, L,
          bs = "cb",
          k = c(3, 25),  #cubic response (at most) to drought, one knot per month lag.
          xt = list(bs = "cr")),
      family = binomial,
      data = demog_post_1ha,
      # gamma = 1.2, #increases smoothness when above 1
      method = "REML")
```
```{r}
summary(s_post_1ha)
```

@@

```{r}
p_surv_cf <-
  pred_s_post_cf %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = plogis(fitted), fill = plogis(fitted))) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:24, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "Month",
      labels = month(ymd("2020-2-01") - months(0:24), label = TRUE))
  ) + 
  scale_x_continuous("SPEI_3", expand = c(0,0)) +
  scale_fill_viridis_c("P(survival)", option = "A", limits = plogis(surv_lim)) +
  labs(title = "Continuous Forest",
       caption = glue("Predicted values for average sized plant ({mean_size} shoots)")) +
  theme_bw()
p_surv_cf
```

```{r}
p_surv_1ha <-
  pred_s_post_1ha %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = plogis(fitted), fill = plogis(fitted))) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:24, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "Month",
      labels = month(ymd("2020-2-01") - months(0:24), label = TRUE))
  ) +
  scale_x_continuous("SPEI_3", expand = c(0,0)) +
  scale_fill_viridis_c("P(survival)", option = "A", limits = plogis(surv_lim)) +
  labs(title = "1-ha Fragments",
       caption = glue("Predicted values for average sized plant ({mean_size} shoots)")) +
  theme_bw()
p_surv_1ha
```

@@

```{r}
p_surv_cf_slice <-
  pred_s_post_cf %>% 
  filter(nearest(x, -1.50)) %>% 
  ggplot(aes(x = lag, y = plogis(fitted))) +
  geom_ribbon(aes(
    ymin = plogis(fitted - se.fit * 1.96),
    ymax = plogis(fitted + se.fit * 1.96)
  ), alpha = 0.3)+
  geom_line() +
  scale_x_continuous("lag(months)", breaks = 0:24) +
  labs(title = "Continuous Forest", y = "P(survival)") +
  theme_linedraw()
p_surv_cf_slice
```

```{r}
p_surv_1ha_slice <-
  pred_s_post_1ha %>% 
  filter(nearest(x, -1.5)) %>% 
  ggplot(aes(x = lag, y = plogis(fitted))) +
  geom_ribbon(aes(
    ymin = plogis(fitted - se.fit * 1.96),
    ymax = plogis(fitted + se.fit * 1.96)
  ), alpha = 0.3)+
  geom_line() +
  scale_x_continuous("lag(months)", breaks = 0:24) +
  labs(title = "1-ha Fragments", y = "P(survival)") +
  theme_linedraw()
p_surv_1ha_slice
```

@@

```{r}
f_post_cf <-
  gam(flwr ~ 
        s(log_shts) +
        s(plot, bs = "re") +
        s(spei_history, L,
          bs = "cb",
          k = c(3, 25),  #cubic response (at most) to drought, one knot per month lag.
          xt = list(bs = "cr")),
      family = binomial,
      data = demog_post_cf,
      # gamma = 1.2, #increases smoothness when above 1
      method = "REML")
```

```{r}
# gam.check(f_post_cf)
```

@@

```{r}
f_post_1ha <-
  gam(flwr ~ 
        s(log_shts) +
        s(plot, bs = "re") +
        s(spei_history, L,
          bs = "cb",
          k = c(3, 25),  #cubic response (at most) to drought, one knot per month lag.
          xt = list(bs = "cr")),
      family = binomial,
      data = demog_post_1ha,
      # gamma = 1.2, #increases smoothness when above 1
      method = "REML")
```

@@

```{r}
p_flowered_cf <-
  pred_f_post_cf %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = plogis(fitted), fill = plogis(fitted))) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:24, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "Month",
      labels = month(ymd("2020-2-01") - months(0:24), label = TRUE))
  ) + 
  scale_x_continuous("SPEI_3", expand = c(0,0)) +
  scale_fill_viridis_c("P(flowering)", option = "A", limits = plogis(flowered_lim)) +
  labs(title = "Continuous Forest") +
  theme_bw()
p_flowered_cf
```

```{r}
p_flowered_1ha <-
  pred_f_post_1ha %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = plogis(fitted), fill = plogis(fitted))) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:24, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "Month",
      labels = month(ymd("2020-2-01") - months(0:24), label = TRUE))
  ) + 
  scale_x_continuous("SPEI_3", expand = c(0,0)) +
  scale_fill_viridis_c("P(flowering)", option = "A", limits = plogis(flowered_lim)) +
  labs(title = "1-ha Fragments") +
  theme_bw()
p_flowered_1ha
```
very similar to growth

@@

```{r}
p_flowered_cf_slice <-
  pred_f_post_cf %>% 
  filter(nearest(x, -1.50)) %>% 
  ggplot(aes(x = lag, y = plogis(fitted))) +
  geom_ribbon(aes(
    ymin = plogis(fitted - se.fit * 1.96),
    ymax = plogis(fitted + se.fit * 1.96)
  ), alpha = 0.3)+
  geom_line() +
  scale_x_continuous("lag(months)", breaks = 0:24) +
  labs(title = "Continuous Forest", y = "P(flowering)") +
  theme_linedraw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
p_flowered_cf_slice
```

```{r}
p_flowered_1ha_slice <-
  pred_f_post_1ha %>% 
  filter(nearest(x, -1.5)) %>% 
  ggplot(aes(x = lag, y = plogis(fitted))) +
  geom_ribbon(aes(
    ymin = plogis(fitted - se.fit * 1.96),
    ymax = plogis(fitted + se.fit * 1.96)
  ), alpha = 0.3)+
  geom_line() +
  scale_x_continuous("lag(months)", breaks = 0:24) +
  labs(title = "1-ha Fragments", y = "P(flowering)") +
  theme_linedraw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
p_flowered_1ha_slice
```

# Plots
## Growth
```{r}
p_growth_spei <-
  (p_growth_cf | p_growth_1ha) +
  plot_annotation(title = "Effect of drought on growth of average sized plant (~2.8 shoots)") +
  plot_layout(guides = "collect") & theme_talk & labs(caption = "")
p_growth_spei
ggsave(here("growth_spei_xa.png"), p_growth_spei, height = 7, width = 14)
```

@@

```{r}
(p_growth_cf_slice + theme(axis.text.x = element_blank())) /
  p_growth_1ha_slice +
  plot_annotation(title = "Effect of severe drought (SPEI = -1.5) on average sized plant (~2.8 shoots)")
ggsave(here("growth slice_xa.png"))
```

@@

```{r}
p_surv_spei <- 
  (p_surv_cf|p_surv_1ha) + 
  plot_annotation(title = "Effect of drought on survival") +
  plot_layout(guides = "collect") & theme_talk & labs(caption="")
p_surv_spei
ggsave(here("surv_spei_xa.png"), p_surv_spei, width = 14, height = 7)
```

@@

```{r}
((p_surv_cf_slice + theme(axis.text.x = element_blank())) / p_surv_1ha_slice) +
  plot_annotation(title = "Effect of severe drought (SPEI = -1.5)")
ggsave(here("survival slice_xa.png"))
```
Pretty flat.

@@

```{r}
p_flowered_spei <- 
  (p_flowered_cf|p_flowered_1ha) + 
  plot_annotation(title = "Effect of drought on flowering") +
  plot_layout(guides = "collect") & theme_talk & labs(caption = "")
p_flowered_spei
ggsave(here("flowering_spei.png"), p_flowered_spei, width = 14, height = 7)
```

@@

```{r}
((p_flowered_cf_slice + theme(axis.text.x = element_blank())) / p_flowered_1ha_slice) +
  plot_annotation(title = "Effect of severe drought (SPEI = -1.5)")
ggsave(here("flowering slice.png"))
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, paged.print=FALSE)
library(tidyverse)
library(here)
library(mgcv)
library(dlnm)
library(bbmle)
library(lubridate)
library(glue)
library(patchwork)
library(sf)
library(tsibble)
library(broom)
library(gratia)

@@

- Switch measure of plant size to shoots * height
- ~~Change lag to 36 months (3 years)~~
- Produce ridge plot

@@

@@

```{r}
demog_full <-
  demog_full %>% 
  mutate(log_shts = log(shts + 0.0001), .after = shts) %>% 
  mutate(log_shts_next = log(shts_next + 0.0001), .after = shts_next) %>% 
  mutate(size = shts*ht, size_next = shts_next*ht_next)
```

@@

```{r}
g_post_cf <-
  gam(shts_next ~ 
        s(log_shts) + 
        s(plot, bs = "re") + #random effect of plot
        s(spei_history, L,
          bs = "cb",
          k = c(3, 35),  #unimodal-ish response to drought, but one knot per month lag.
          xt = list(bs = "cr")),
      family = poisson(link = "log"),
      # family = scat(link = "log"), #like leptokurtic gaussian.
      data = demog_post_cf,
      # gamma = 1.2, #I maybe need to optimize this with cross-validation?
      method = "REML")
```

@@

```{r}
appraise(g_post_cf)
```

@@

```{r}
g_post_1ha <-
  gam(shts_next ~ 
        s(log_shts) +
        s(plot, bs = "re") +
        s(spei_history, L,
          bs = "cb",
          k = c(3, 35),  #unimodal response to drought, but one knot per month lag.
          xt = list(bs = "cr")),
      # family = poisson(link = "log"),
      # family = quasipoisson(link = "log"),
      family = gaussian(link = "log"),
      # family = scat(link = "log"), #like leptokurtic gaussian.
      data = demog_post_1ha,
      # gamma = 1.2, #increases smoothness when above 1
      method = "REML")
```

```{r}
appraise(g_post_1ha)
```

@@

```{r}
p_growth_cf <-
  pred_g_post_cf %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = exp(fitted), fill = exp(fitted))) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:36, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "Month",
      labels = month(ymd("2020-2-01") - months(0:36), label = TRUE))
  ) +
  scale_x_continuous("SPEI_3", expand = c(0,0)) +
  scale_fill_viridis_c("#shoots (t+1)", option = "A", limits = exp(shoot_lim)) +
  labs(title = "Continuous Forest",
       caption = glue("Predicted values for average sized plant ({mean_size} shoots)")) +
  theme_bw()
p_growth_cf
```

```{r}
p_growth_1ha <-
  pred_g_post_1ha %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = exp(fitted), fill = exp(fitted))) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:36, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "Month",
      labels = month(ymd("2020-2-01") - months(0:36), label = TRUE))
  ) +  scale_x_continuous("SPEI_3", expand = c(0,0)) +
  scale_fill_viridis_c("#shoots (t+1)", option = "A", limits = exp(shoot_lim)) +
  labs(title = "1-ha Fragments",
       caption = glue("Predicted values for average sized plant ({mean_size} shoots)")) +
  theme_bw()
p_growth_1ha
```

@@

```{r}
p_growth_cf_slice <-
  pred_g_post_cf %>% 
  filter(nearest(x, -1.50)) %>% 
  ggplot(aes(x = lag, y = exp(fitted))) +
  geom_ribbon(aes(
    ymin = exp(fitted - se.fit * 1.96),
    ymax = exp(fitted + se.fit * 1.96)
  ), alpha = 0.3)+
  geom_line() +
  scale_x_continuous("lag(months)", breaks = 0:36) +
  labs(title = "Continuous Forest", y = "shoots (t+1)") +
  theme_linedraw()
p_growth_cf_slice
```

```{r}
p_growth_1ha_slice <-
  pred_g_post_1ha %>% 
  filter(nearest(x, -1.5)) %>% 
  ggplot(aes(x = lag, y = exp(fitted))) +
  geom_ribbon(aes(
    ymin = exp(fitted - se.fit * 1.96),
    ymax = exp(fitted + se.fit * 1.96)
  ), alpha = 0.3)+
  geom_line() +
  scale_x_continuous("lag(months)", breaks = 0:36) +
  labs(title = "1-ha Fragments", y = "shoots (t+1)") +
  theme_linedraw()
p_growth_1ha_slice
```

@@

```{r}
s_post_cf <-
  gam(surv ~ 
        s(log_shts) +
        s(plot, bs = "re") +
        s(spei_history, L,
          bs = "cb",
          k = c(3, 35),  #cubic response (at most) to drought, one knot per month lag.
          xt = list(bs = "cr")),
      family = binomial,
      data = demog_post_cf,
      # gamma = 1.2, #increases smoothness when above 1
      method = "REML")
```
```{r}
# gam.check(s_post_cf) #not sure what to expect from any of these plots
appraise(s_post_cf)
```
```{r}
summary(s_post_cf)
```

```{r}
s_post_1ha <-
  gam(surv ~ 
        s(log_shts) +
        s(plot, bs = "re") +
        s(spei_history, L,
          bs = "cb",
          k = c(3, 35),  #cubic response (at most) to drought, one knot per month lag.
          xt = list(bs = "cr")),
      family = binomial,
      data = demog_post_1ha,
      # gamma = 1.2, #increases smoothness when above 1
      method = "REML")
```
```{r}
summary(s_post_1ha)
```

@@

```{r}
p_surv_cf <-
  pred_s_post_cf %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = plogis(fitted), fill = plogis(fitted))) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:36, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "Month",
      labels = month(ymd("2020-2-01") - months(0:36), label = TRUE))
  ) + 
  scale_x_continuous("SPEI_3", expand = c(0,0)) +
  scale_fill_viridis_c("P(survival)", option = "A", limits = plogis(surv_lim)) +
  labs(title = "Continuous Forest",
       caption = glue("Predicted values for average sized plant ({mean_size} shoots)")) +
  theme_bw()
p_surv_cf
```

```{r}
p_surv_1ha <-
  pred_s_post_1ha %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = plogis(fitted), fill = plogis(fitted))) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:36, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "Month",
      labels = month(ymd("2020-2-01") - months(0:36), label = TRUE))
  ) +
  scale_x_continuous("SPEI_3", expand = c(0,0)) +
  scale_fill_viridis_c("P(survival)", option = "A", limits = plogis(surv_lim)) +
  labs(title = "1-ha Fragments",
       caption = glue("Predicted values for average sized plant ({mean_size} shoots)")) +
  theme_bw()
p_surv_1ha
```

@@

```{r}
p_surv_cf_slice <-
  pred_s_post_cf %>% 
  filter(nearest(x, -1.50)) %>% 
  ggplot(aes(x = lag, y = plogis(fitted))) +
  geom_ribbon(aes(
    ymin = plogis(fitted - se.fit * 1.96),
    ymax = plogis(fitted + se.fit * 1.96)
  ), alpha = 0.3)+
  geom_line() +
  scale_x_continuous("lag(months)", breaks = 0:36) +
  labs(title = "Continuous Forest", y = "P(survival)") +
  theme_linedraw()
p_surv_cf_slice
```

```{r}
p_surv_1ha_slice <-
  pred_s_post_1ha %>% 
  filter(nearest(x, -1.5)) %>% 
  ggplot(aes(x = lag, y = plogis(fitted))) +
  geom_ribbon(aes(
    ymin = plogis(fitted - se.fit * 1.96),
    ymax = plogis(fitted + se.fit * 1.96)
  ), alpha = 0.3)+
  geom_line() +
  scale_x_continuous("lag(months)", breaks = 0:36) +
  labs(title = "1-ha Fragments", y = "P(survival)") +
  theme_linedraw()
p_surv_1ha_slice
```

@@

```{r}
f_post_cf <-
  gam(flwr ~ 
        s(log_shts) +
        s(plot, bs = "re") +
        s(spei_history, L,
          bs = "cb",
          k = c(3, 35),  #cubic response (at most) to drought, one knot per month lag.
          xt = list(bs = "cr")),
      family = binomial,
      data = demog_post_cf,
      # gamma = 1.2, #increases smoothness when above 1
      method = "REML")
```

```{r}
appraise(f_post_cf)
```

@@

```{r}
f_post_1ha <-
  gam(flwr ~ 
        s(log_shts) +
        s(plot, bs = "re") +
        s(spei_history, L,
          bs = "cb",
          k = c(3, 35),  #cubic response (at most) to drought, one knot per month lag.
          xt = list(bs = "cr")),
      family = binomial,
      data = demog_post_1ha,
      # gamma = 1.2, #increases smoothness when above 1
      method = "REML")
```

```{r}
appraise(f_post_1ha)
```

@@

```{r}
p_flowered_cf <-
  pred_f_post_cf %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = plogis(fitted), fill = plogis(fitted))) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:36, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "Month",
      labels = month(ymd("2020-2-01") - months(0:36), label = TRUE))
  ) + 
  scale_x_continuous("SPEI_3", expand = c(0,0)) +
  scale_fill_viridis_c("P(flowering)", option = "A", limits = plogis(flowered_lim)) +
  labs(title = "Continuous Forest") +
  theme_bw()
p_flowered_cf
```

```{r}
p_flowered_1ha <-
  pred_f_post_1ha %>%
  filter(min_dist < 0.1) %>%
  ggplot(aes(x = x, y = lag, z = plogis(fitted), fill = plogis(fitted))) +
  geom_raster(interpolate = TRUE) +
  scale_y_continuous(
    "lag (months)",
    breaks = 0:36, 
    expand = c(0,0),
    sec.axis = dup_axis(
      name = "Month",
      labels = month(ymd("2020-2-01") - months(0:36), label = TRUE))
  ) + 
  scale_x_continuous("SPEI_3", expand = c(0,0)) +
  scale_fill_viridis_c("P(flowering)", option = "A", limits = plogis(flowered_lim)) +
  labs(title = "1-ha Fragments") +
  theme_bw()
p_flowered_1ha
```
very similar to growth

@@

```{r}
p_flowered_cf_slice <-
  pred_f_post_cf %>% 
  filter(nearest(x, -1.50)) %>% 
  ggplot(aes(x = lag, y = plogis(fitted))) +
  geom_ribbon(aes(
    ymin = plogis(fitted - se.fit * 1.96),
    ymax = plogis(fitted + se.fit * 1.96)
  ), alpha = 0.3)+
  geom_line() +
  scale_x_continuous("lag(months)", breaks = 0:36) +
  labs(title = "Continuous Forest", y = "P(flowering)") +
  theme_linedraw() 
p_flowered_cf_slice
```

```{r}
p_flowered_1ha_slice <-
  pred_f_post_1ha %>% 
  filter(nearest(x, -1.5)) %>% 
  ggplot(aes(x = lag, y = plogis(fitted))) +
  geom_ribbon(aes(
    ymin = plogis(fitted - se.fit * 1.96),
    ymax = plogis(fitted + se.fit * 1.96)
  ), alpha = 0.3)+
  geom_line() +
  scale_x_continuous("lag(months)", breaks = 0:36) +
  labs(title = "1-ha Fragments", y = "P(flowering)") +
  theme_linedraw()
p_flowered_1ha_slice
```

# Plots
## Growth
```{r}
p_growth_spei <-
  (p_growth_cf | p_growth_1ha) +
  plot_annotation(title = "Effect of drought on growth of average sized plant (~2.8 shoots)") +
  plot_layout(guides = "collect") & theme_talk & labs(caption = "")
p_growth_spei
ggsave(here("analysis", "figures", "growth_spei.png"), p_growth_spei, height = 7, width = 14)
```

@@

```{r}
(p_growth_cf_slice + theme(axis.text.x = element_blank())) /
  p_growth_1ha_slice +
  plot_annotation(title = "Effect of severe drought (SPEI = -1.5) on average sized plant (~2.8 shoots)")
ggsave(here("analysis", "figures", "growth slice.png"))
```

@@

```{r}
p_surv_spei <- 
  (p_surv_cf|p_surv_1ha) + 
  plot_annotation(title = "Effect of drought on survival") +
  plot_layout(guides = "collect") & theme_talk & labs(caption="")
p_surv_spei
ggsave(here("analysis", "figures", "surv_spei.png"), p_surv_spei, width = 14, height = 7)
```

@@

```{r}
((p_surv_cf_slice + theme(axis.text.x = element_blank())) / p_surv_1ha_slice) +
  plot_annotation(title = "Effect of severe drought (SPEI = -1.5)")
ggsave(here("analysis", "figures", "survival slice.png"))
```
Pretty flat.

@@

```{r}
p_flowered_spei <- 
  (p_flowered_cf|p_flowered_1ha) + 
  plot_annotation(title = "Effect of drought on flowering") +
  plot_layout(guides = "collect") & theme_talk & labs(caption = "")
p_flowered_spei
ggsave(here("analysis", "figures", "flowering_spei.png"), p_flowered_spei, width = 14, height = 7)
```

@@

```{r}
((p_flowered_cf_slice + theme(axis.text.x = element_blank())) / p_flowered_1ha_slice) +
  plot_annotation(title = "Effect of severe drought (SPEI = -1.5)")
ggsave(here("analysis", "figures", "flowering slice.png"))
```
